### 2013-03-28 doc/sosp13/evaluation.tex
edits
add histograms
ev

In summary, our context switch engine is able to efficiently sustain very high
concurrency and as we will show later, the amount of concurrency sustained is
sufficient the latencies \Grappa needs to hide.

@@

>>>>

In summary, our context switch engine is able to efficiently sustain very high
concurrency and as we will show later, the amount of concurrency sustained is
sufficient for the latencies \Grappa needs to hide.

@@

\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{results/histograms/latency_cmb.pdf}
    \end{center}
    \caption{Round-trip latency of delegate operations.}
%bar chart, one set of bars per benchmark, one bar per system. runtime normalized to grappa.
    \label{fig:grappa-latency}
\end{figure}

\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{results/histograms/rdma_bytes_sent_histogram_cmb.pdf}
    \end{center}
    \caption{Distribution of aggregated message sizes.}
%bar chart, one set of bars per benchmark, one bar per system. runtime normalized to grappa.
    \label{fig:grappa-message-size}
\end{figure}
